Concurrent Programming in Harmony

### 2020-09-28 book/paper.tex
Fixed typo

So we are looking for an inductive invariant that \emph{implies} exclusivity.
In other words, the set of states where the inductive invariant holds
must be a subset of the set of states where there is at most one process in
the critical section.
For simplicity, we will suppose as a given that 
$\mathtt{process}(i)@cs \Rightarrow \mathit{flags][i]$, the truth of which is
easy to see from the code.
Let $\mathcal{C}(i) = \lnot\mathit{flags}[1 - i] \lor
\mathit{turn} = i$, that is, the condition on the \textbf{await}
statement for process~$i$.
Let predicate $\mathcal{I}_p(i)$ be the following:
if process $i$ is at label \texttt{@cs} (i.e., process $i$ is in the critical section),
then $\mathcal{C}(i)$ holds or process $1-i$ is executing after setting
$\mathit{flags}[i]$ but still before setting \textit{turn} to $1-i$.
More formally, $\mathcal{I}_p(i) = \mathtt{process}(i)@cs \Rightarrow \mathcal{C}(i) \lor \mathtt{process}(1-i)@gate$.
For Peterson's Algorithm, an inductive invariant that works well is
$\mathcal{I}_p(0) \land \mathcal{I}_p(1)$.

>>>>

So we are looking for an inductive invariant that \emph{implies} exclusivity.
In other words, the set of states where the inductive invariant holds
must be a subset of the set of states where there is at most one process in
the critical section.
For simplicity, we will suppose as a given that 
$\mathtt{process}(i)@cs \Rightarrow \mathit{flags}[i]$, the truth of which is
easy to see from the code.
Let $\mathcal{C}(i) = \lnot\mathit{flags}[1 - i] \lor
\mathit{turn} = i$, that is, the condition on the \textbf{await}
statement for process~$i$.
Let predicate $\mathcal{I}_p(i)$ be the following:
if process $i$ is at label \texttt{@cs} (i.e., process $i$ is in the critical section),
then $\mathcal{C}(i)$ holds or process $1-i$ is executing after setting
$\mathit{flags}[i]$ but still before setting \textit{turn} to $1-i$.
More formally, $\mathcal{I}_p(i) = \mathtt{process}(i)@cs \Rightarrow \mathcal{C}(i) \lor \mathtt{process}(1-i)@gate$.
For Peterson's Algorithm, an inductive invariant that works well is
$\mathcal{I}_p(0) \land \mathcal{I}_p(1)$.
